%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Embedded Software Consultant} % Job title
    {Savoir-Faire Linux} % Organization
    {Montreal, Quebec} % Location
    {April 2013 - September 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\textbf{Projects Management}}
          \begin{itemize}
            \item{Designed Firmwares architecture based on customer needs.}
            \item{Estimate and regular update on projects with customers using the \textit{Agile} methodology.}
            \item{Supervision of a small team of 3 people with daily \textit{Scrum} meeting}
          \end{itemize}
        \item{\textbf{Linux Firmwares Development}}
          \begin{itemize}
            \item{Developed Firmwares based on \textit{Buildroot}, \textit{Yocto} and \textit{OpenWRT} solutions.}
            \item{Wrote \textit{C} user space softwares to interact with the hardware.}
            \item{Wrote \textit{Python / Bash} scripts to automate Firmware initialization, and recovery (e.g. \textit{ROOTFS} checksummer, devices specific partition initialization and recovery).}
            \item{Definition and writing of secure \textit{OTA} mechanism.}
            \item{Wrote \textit{Linux} devices drivers (e.g. Watchdog driver, custom \textit{FPGA} driver and \textit{FPGA} bus driver, \textit{LED} driver, \textit{SPI-NOR} flash driver, and so on...)}
            \item{\textit{Linux} Kernel configuration, \textit{Linux} Kernel Device Tree and Board support package wrote for few board, mainly \textit{ARM} \textit{Cortex A8} and \textit{A7} \textit{SoC} (\textit{AllWinner A20}, \textit{AM335x}, \textit{TS4100}, \textit{TS4600}, \textit{TS4900} series, etc...)}
            \item{Configuring and modifying the \textit{U-Boot} bootloader, and writing new \textit{U-Boot} device drivers.}
          \item{Implemented \textit{JIG} tests for \textit{Allwinner A20 SoC} (\textit{Cortex A7}) to ensure production validity} 
          \item{Debugging and profiling client softwares, detecting bottlenecks and performance issues using wide range of tools like \textit{Valgrind, Oprofile, GDB}...}
        \end{itemize}
      \item{\textbf{MCU Firmwares Development}}
        \begin{itemize}
          \item{Wrote \textit{FreeRTOS} firmware for an \textit{STM32F3 MCU}.}
          \item{Wrote a firmware for an \textit{STM32F3 MCU} using the \textit{Zephyr RTOS}.}
          \item{Refactored and debug Baremetal \textit{RTOS} for an \textit{LPC} and \textit{AVR MCU}.}
          \item{Refactoring, Debugging and implementation of unit tests with \textit{CMocka} on a \textit{FreeRTOS} Firmware, used to scan \textit{RFID} Tags, improves scanning speed by 10\%.}
        \end{itemize}
      \item{\textbf{Open Source Projects contributions}}
        \begin{itemize}
          \item{\href{https://patchwork.kernel.org/project/linux-arm-kernel/list/?submitter=92211&archive=both}{Contribute to the \textit{Linux} Kernel project. \faExternalLink}}
          \item{\href{https://github.com/zephyrproject-rtos/zephyr/commits?author=sbourdelin}{Contribute to the \textit{Zephyr RTOS} project. \faExternalLink}}
          \item{\href{http://u-boot.10912.n7.nabble.com/template/NamlServlet.jtp?macro=user_nodes&user=8888}{Contribute to the \textit{U-Boot} bootloader project. \faExternalLink}}
          \item{\href{http://buildroot-busybox.2317881.n4.nabble.com/template/NamlServlet.jtp?macro=user_nodes&user=1269}{Contribute to the \textit{Buildroot} project. \faExternalLink}}
          \item{\href{https://www.sigrok.org/blog/new-protocol-decoder-pwm}{Contribute to \textit{Sigrok} an open source logical analyzeur project. \faExternalLink}}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Developer} % Job title
    {SFR-Numéricable, Efixo.} % Organization
    {Marseille, France} % Location
    {Mars 2010 - January 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Firmware development for \textit{Neufbox 6} and \textit{Neufbox 6V}.\newline
          Which are \textit{ADSL} and \textit{VDSL2} routers / modems based on \textit{OpenWRT}.\newline
          The product was developed within a team of 6 people and has been used in tens of thousands of homes.}
        \item {Porting a manufacturer board support package to Linux for the \textit{Neufbox 6} board which included support for the \textit{ADSL/VDSL2} chip, Switch \textit{RTL8367RB}, Nand, USB...}
        \item {Modify the \textit{CFE} Bootloder to introduce an hidden version number in the \textit{JFFS2} \textit{OOB} section of a NAND memory.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
